msc dissertation

### 2021-08-24 index.Rmd
latest

@@

ggplot(zsummary, aes(x = condition, y = percent, fill = forcats::fct_rev(headlineveracity))) + 
  geom_bar(stat = 'identity',position = 'dodge',width = 0.5) + 
  geom_text(
    aes(label = sprintf("%.2f",percent)), vjust = 2.5, position = position_dodge(0.5)) +
  xlab("Condition") + 
  ylab("Likelihood of Sharing (%)") +
  scale_x_discrete(labels= c("0"="Control","1"="Treatment"))+
  scale_fill_manual(values = c("orange2","forestgreen"), name = "Headline Veracity", labels = c("True", "False")) + labs(title = "All Subjects") + 
  geom_errorbar(aes(ymin = lowci, ymax = upci,width = 0.2),position = position_dodge(0.5), size = 0.6)

@@

```{r, message=FALSE}
#Ordinal logistic regression

library(ordinal)
library(ggeffects)
library(ggrepel)

@@

str(ordinaldata)
ordinaldata$measurement <- as.factor(ordinaldata$measurement)

ordinal <- clm(measurement ~ condition + condition*headlineveracity, data = ordinaldata, link = "logit")

@@

@@

ggplot(ggpredict_ordinaldata, aes(x = Rating, y = predicted)) + 
  geom_point(aes(color = Headlineveracity), position =position_dodge(width = 0.5)) + geom_errorbar(aes(ymin = conf.low, ymax = conf.high, color = Headlineveracity), position = position_dodge(width = 0.5), width = 0.3) + 
  theme_minimal() + facet_wrap(~group) + xlab("Likelihood of Sharing") + ylab("Predicted Probability of Sharing") + labs(title = "All Subjects")

  + geom_label_repel(aes(label=sprintf("%.3f", predicted),fill = Headlineveracity), box.padding = 0.5, min.segment.length = unit(0, 'lines'), size = 3) #this gives you the box label of each points

@@

ordinal1 <- clm(measurement ~ condition + condition*headlineveracity, data = ordinaldata1, link = "logit")

@@

ggplot(ggpredict_ordinaldata1, aes(x = Rating, y = predicted)) + 
  geom_point(aes(color = Headlineveracity), position =position_dodge(width = 0.5)) + geom_errorbar(aes(ymin = conf.low, ymax = conf.high, color = Headlineveracity), position = position_dodge(width = 0.5), width = 0.3) + 
  theme_minimal() + facet_wrap(~group) + xlab("Likelihood of Sharing") + ylab("Predicted Probability of Sharing") + labs(title = "\u2265 1 Screener Correct")

 + geom_label_repel(aes(label=sprintf("%.3f", predicted),fill = Headlineveracity), box.padding = 0.5, min.segment.length = unit(0, 'lines'), size = 3)

@@

ordinal2 <- clm(measurement ~ condition + condition*headlineveracity, data = ordinaldata2, link = "logit")

@@

ggplot(ggpredict_ordinaldata2, aes(x = Rating, y = predicted)) + 
  geom_point(aes(color = Headlineveracity), position =position_dodge(width = 0.5)) + geom_errorbar(aes(ymin = conf.low, ymax = conf.high, color = Headlineveracity), position = position_dodge(width = 0.5), width = 0.3) + 
  theme_minimal() + facet_wrap(~group) + xlab("Likelihood of Sharing") + ylab("Predicted Probability of Sharing")  + labs(title = "\u2265 2 Screener Correct")

 + geom_label_repel(aes(label=sprintf("%.3f", predicted),fill = Headlineveracity), box.padding = 0.5, min.segment.length = unit(0, 'lines'), size = 3)

@@

ordinal3 <- clm(measurement ~ condition + condition*headlineveracity, data = ordinaldata3, link = "logit")

@@

ggplot(ggpredict_ordinaldata3, aes(x = Rating, y = predicted)) + 
  geom_point(aes(color = Headlineveracity), position =position_dodge(width = 0.5)) + geom_errorbar(aes(ymin = conf.low, ymax = conf.high, color = Headlineveracity), position = position_dodge(width = 0.5), width = 0.3) + 
  theme_minimal() + facet_wrap(~group) + xlab("Likelihood of Sharing") + ylab("Predicted Probability of Sharing") + labs(title = "All 3 Screener Correct")

 + geom_label_repel(aes(label=sprintf("%.3f", predicted),fill = Headlineveracity), box.padding = 0.55, min.segment.length = unit(0, 'lines'), size = 2.5)

>>>>

#rename the columns for make it clear

@@

ggplot(zsummary, aes(x = condition, y = percent, fill = forcats::fct_rev(headlineveracity))) + 
  geom_bar(stat = 'identity',position = 'dodge',width = 0.5) + 
  geom_text(
    aes(label = sprintf("%.2f",percent)), vjust = 2.5, position = position_dodge(0.5)) +
  xlab("Condition") + 
  ylab("Likelihood of Sharing (%)") +
  scale_x_discrete(labels= c("0"="Control","1"="Treatment"))+
  scale_fill_manual(values = c("orange2","forestgreen"), name = "Headline Veracity", labels = c("True", "False")) + labs(title = "All Subjects") + 
  geom_errorbar(aes(ymin = lowci, ymax = upci,width = 0.2),position = position_dodge(0.5), size = 0.6) + 
  theme( axis.title.x = element_text(size=14, face="bold"),
axis.title.y = element_text( size=14, face="bold"), axis.text.x = element_text(size = 14, face="bold"),axis.text.y = element_text(size = 14, face="bold"))

@@

```{r, message=FALSE}
#Ordinal logistic regression
library(ordinal)
library(ggeffects)
library(ggrepel)

@@

#change measurement to factor
str(ordinaldata)
ordinaldata$measurement <- as.factor(ordinaldata$measurement)

#model equation
ordinal <- clm(measurement ~ headlineveracity + condition*headlineveracity, data = ordinaldata, link = "logit")

@@

#ggpredict change log odds to probabilities

@@

#plot the graph
ggplot(ggpredict_ordinaldata, aes(x = Rating, y = predicted)) + 
  geom_point(aes(color = Headlineveracity), position =position_dodge(width = 0.5)) + geom_errorbar(aes(ymin = conf.low, ymax = conf.high, color = Headlineveracity), position = position_dodge(width = 0.5), width = 0.3) + 
  theme_minimal() + facet_wrap(~group) + xlab("Likelihood of Sharing") + ylab("Predicted Probability of giving such rating") + labs(title = "All Subjects") + geom_label_repel(aes(label=sprintf("%.3f", predicted),fill = Headlineveracity), box.padding = 0.5, min.segment.length = unit(0, 'lines'), size = 3) #this gives you the box label of each points

@@

ordinal1 <- clm(measurement ~ headlineveracity + condition*headlineveracity, data = ordinaldata1, link = "logit")

@@

ggplot(ggpredict_ordinaldata1, aes(x = Rating, y = predicted)) + 
  geom_point(aes(color = Headlineveracity), position =position_dodge(width = 0.5)) + geom_errorbar(aes(ymin = conf.low, ymax = conf.high, color = Headlineveracity), position = position_dodge(width = 0.5), width = 0.3) + 
  theme_minimal() + facet_wrap(~group) + xlab("Likelihood of Sharing") + ylab("Predicted Probability of giving such rating") + labs(title = "\u2265 1 Screener Correct") + geom_label_repel(aes(label=sprintf("%.3f", predicted),fill = Headlineveracity), box.padding = 0.5, min.segment.length = unit(0, 'lines'), size = 3)

@@

ordinal2 <- clm(measurement ~ headlineveracity + condition*headlineveracity, data = ordinaldata2, link = "logit")

@@

ggplot(ggpredict_ordinaldata2, aes(x = Rating, y = predicted)) + 
  geom_point(aes(color = Headlineveracity), position =position_dodge(width = 0.5)) + geom_errorbar(aes(ymin = conf.low, ymax = conf.high, color = Headlineveracity), position = position_dodge(width = 0.5), width = 0.3) + 
  theme_minimal() + facet_wrap(~group) + xlab("Likelihood of Sharing") + ylab("Predicted Probability of giving such rating")  + labs(title = "\u2265 2 Screener Correct") + geom_label_repel(aes(label=sprintf("%.3f", predicted),fill = Headlineveracity), box.padding = 0.5, min.segment.length = unit(0, 'lines'), size = 3)

@@

ordinal3 <- clm(measurement ~ headlineveracity + condition*headlineveracity, data = ordinaldata3, link = "logit")

@@

ggplot(ggpredict_ordinaldata3, aes(x = Rating, y = predicted)) + 
  geom_point(aes(color = Headlineveracity), position =position_dodge(width = 0.5)) + geom_errorbar(aes(ymin = conf.low, ymax = conf.high, color = Headlineveracity), position = position_dodge(width = 0.5), width = 0.3) + 
  theme_minimal() + facet_wrap(~group) + xlab("Likelihood of Sharing") + ylab("Predicted Probability of giving such rating") + labs(title = "All 3 Screener Correct") + geom_label_repel(aes(label=sprintf("%.3f", predicted),fill = Headlineveracity), box.padding = 0.55, min.segment.length = unit(0, 'lines'), size = 2.5)
